### 2013-02-24 article.tex
Spell check
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>

We have released Genomer as open source on GitHub \cite{genomer-github} and
have prepared documentation and video tutorials at http://next.gs. As we have
used this tool extensively to simplify our own genome projects we believe
genomer may also be useful to others in the field. A practice described as
``eating your own dog food'' \cite{harrison2006}. We will illustrate the
possible usefulness of genomer with two use cases: updating the annotations of
a genome scaffold during the finishing process, and preparing genome files for
submission to Genbank.

@@

Genome annotation is required to identify the features responsible for
phenotype. Online tools such as the Integrated Microbial Genomes system
\cite{markowitz2006} provide an online service whereby a nucleotide sequence
may be submitted and a subsequent file of predicted genomic features returned.
These annotations are required when submitting a genome sequence to a database.
Once annotated modifying the sequence becomes problematic as this requires
corresponding changes in all downstream annotated coordinates. This therefore
presents a problem whereby either no more updates can be made to the sequence
or the delta difference in annotation coordinates must be propagated to all
downstream locations. The former option is often choosen as being simpler and
therefore the genome sequence must be considered `frozen' once annotated and no
more changes can be made.

@@

\subsection*{Second Use Case: Preparing files for submission to Genbank}

Generating a usable genome sequence requires sequencing, assembly of reads, and
annotation. A further step is also required: preparation of genomic files for
deposition in a database. An example is the Genbank database which requires the
genome annotations to be prepared in a custom table format. Additional files
are also required when the genome assembly is incomplete: a FASTA file
containing the individual contig sequences and `a golden path' (AGP)
\cite{agp-spec} file which describes the placement and direction of constituent
contigs in the draft genome sequence. The requirements to generate these
specific files can be time-consuming to complete and difficult to understand
for researchers new to field. We therefore Genomer during our own genome
projects to simplify and automate this process.

@@

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}

>>>>

We have released Genomer as open source on GitHub \cite{genomer-github} and
have prepared documentation and video tutorials at http://next.gs. As we have
used this tool extensively to simplify our own genome projects we believe
genomer may also be useful to others in the field. A practice described as
``eating your own dog food'' \cite{harrison2006}. We will illustrate the
possible usefulness of genomer with two use cases: updating the annotations of
a genome scaffold during the finishing process, and preparing genome files for
submission to GenBank.

@@

Genome annotation is required to identify the features responsible for
phenotype. Online tools such as the Integrated Microbial Genomes system
\cite{markowitz2006} provide an online service whereby a nucleotide sequence
may be submitted and a subsequent file of predicted genomic features returned.
These annotations are required when submitting a genome sequence to a database.
Once annotated modifying the sequence becomes problematic as this requires
corresponding changes in all downstream annotated coordinates. This therefore
presents a problem whereby either no more updates can be made to the sequence
or the delta difference in annotation coordinates must be propagated to all
downstream locations. The former option is often chosen as being simpler and
therefore the genome sequence must be considered `frozen' once annotated and no
more changes can be made.

@@

\subsection*{Second Use Case: Preparing files for submission to GenBank}

Generating a usable genome sequence requires sequencing, assembly of reads, and
annotation. A further step is also required: preparation of genomic files for
deposition in a database. An example is the GenBank database which requires the
genome annotations to be prepared in a custom table format. Additional files
are also required when the genome assembly is incomplete: a FASTA file
containing the individual contig sequences and `a golden path' (AGP)
\cite{agp-spec} file which describes the placement and direction of constituent
contigs in the draft genome sequence. The requirements to generate these
specific files can be time-consuming to complete and difficult to understand
for researchers new to field. We therefore Genomer during our own genome
projects to simplify and automate this process.

@@

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgements}
